Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-05-10 ms.Rmd
Added export table from main MS so that all table can quickly be brought into the supp and rendered all together

table1 <- as.data.frame(rbind(robust_ConspicDisplayAC_CI,
                robust_ConspicDisplayCC_CI,
                robust_ConspicCourtshipAC_CI,
                robust_ConspicCourtshipCC_CI))
table1$Parameter <- rownames(table1)
rownames(table1) <- NULL
# Clean
 final_T1 <- table1 %>% 
             mutate(SocialContext = c("Male-Male Display", rep("", 5), "Courtship Display", rep("", 5)),
                    VisualRealm = c("Achromatic Contrast", rep("", 2), "Chromatic Contrast", rep("", 2), "Achromatic Contrast", rep("", 2), "Chromatic Contrast", rep("", 2))) %>%
              select(SocialContext, VisualRealm, Parameter, beta, SE, df, CI_L, CI_U)

@@

# Clean
 final_T2 <- table2 %>% 
             mutate(JND = c("Achromatic Contrast", rep("", 3), "Chromatic Contrast", rep("", 3))) %>%
              select(JND, Parameter, beta, SE, df, CI_L, CI_U)

 # Table
table2 <- flextable(final_T2) %>%
           table_style7()

@@

@@

table4 <- flextable(tb4) %>% table_style9()
table4
```

>>>>

table1 <- as.data.frame(rbind(robust_ConspicDisplayAC_CI,
                robust_ConspicDisplayCC_CI,
                robust_ConspicCourtshipAC_CI,
                robust_ConspicCourtshipCC_CI))
table1$Parameter <- rownames(table1)
rownames(table1) <- NULL
# Clean
 final_T1 <- table1 %>% 
             mutate(SocialContext = c("Male-Male Display", rep("", 5), "Courtship Display", rep("", 5)),
                    VisualRealm = c("Achromatic Contrast", rep("", 2), "Chromatic Contrast", rep("", 2), "Achromatic Contrast", rep("", 2), "Chromatic Contrast", rep("", 2))) %>%
              select(SocialContext, VisualRealm, Parameter, beta, SE, df, CI_L, CI_U)
 write.csv(final_T1, file = "./output/tables/Table1_MS.csv", row.names = FALSE)

@@

# Clean
 final_T2 <- table2 %>% 
             mutate(JND = c("Achromatic Contrast", rep("", 3), "Chromatic Contrast", rep("", 3))) %>%
              select(JND, Parameter, beta, SE, df, CI_L, CI_U)
 write.csv(final_TT, file = "./output/tables/Table2_MS.csv", row.names = FALSE)
 # Table
table2 <- flextable(final_T2) %>%
           table_style7()

@@

write.csv(contrast, file = "./output/tables/Table3_MS.csv", row.names = FALSE)

@@

write.csv(tb4, file = "./output/tables/Table4_MS.csv", row.names = FALSE)
table4 <- flextable(tb4) %>% table_style9()
table4
```
